Simulation and visualization framework for decision making of climate mitigation \vspace{4pt} and adaptation strategies in new and existing urban development

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex

This study will test the performance of eight strategies alongside one development pathway and two climate change pathways, simulated at two points in time (2050 and 2080), for a case study community in southwestern Canada; Wesbrook Village, Vancouver, British Columbia (BC). A baseline urban building energy model (UBEM) was created to represent the development of the community to-date, shown in Figure \ref{fig:wesbrook_base} alongside the future development and climate change pathways.

@@

\subsection*{Wesbrook Village} 
Simulation will be exhaustive of the different combinations in the pool of strategies and scenarios allowing each strategy to be measured independently as well as determine combinations that are more or less efficient than individual implementation under the entire range of uncertainty, diagrammed in Figure \ref{fig:sample_sequence}.

Wesbrook Village and the neighbouring Stadium Road are new communities that expected to reach 715,925 sqm. of residential floor space and 10,000 sqm. of non-residential floor space by 2040. It is the part of a larger community plan led by the development arm of The University of British Columbia (UBC) \citep{ubc_planning_ubc_2020_SR, ubc_planning_ubc_2020_wb}. The baseline for this study is taken at the end of 2020, where the development has completed its fifteenth year. The development, referred to throughout the study as \textit{Wesbrook}, is a compelling case study as it can be considered a model of medium-density new development for BC and North America at large. Building code for the community is modeled after the aspirational provincial code made more strict through a continuous review with the most recent version taking effect in January 2021 and targeting net-zero energy ready (NZER) by 2032; NZER buildings are built such that with the addition of solar panels or renewable technologies they would consume only as much energy as they produce. The energy system is a mixture of grid-connected systems, in building natural gas boilers, and a district heating system that supplies hydronic baseboard and floor heating systems as well as domestic hot water. This district heating system, described in the context of a UBEM in \citet{mccarty_accepted_2020}, is designed to switch from natural gas boilers to heat pumps amplified by waste heat from a nearby particle accelerator facility but still with peaking boilers fueled by natural gas. Cooling services have yet to considered in spec-residential development in BC as the climate has historically allowed comfort to be achieved in the peak of summer through natural ventilation; research however indicates that this may become an obsolete design standard due to climate change \citep{rysanek_forecasting_2021}. The intention with the code development for this community is that cooling will be required within a decade \citep{noauthor_residential_2021}.

@@

\subsection*{Urban Building Energy Model}
The simulation framework utilizes an extension of the City Energy Analyst (CEA) demand forecasting model \citep{fonseca_integrated_2015,fonseca_city_2016,the_cea_team_city_2020}. The CEA enables simulations of urban and neighborhood scale energy systems, as well as independently operating buildings. It is a hybrid dynamic statistical model that allows for efficient processing times, a necessity for large simulation sets such as the one in this study. These urban building energy models (UBEM) are low-level of detail geometrically described by their heights above and below ground, window to wall ratio, and composition of envelope, HVAC, and energy supply traits.

@@

The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models \citep{oneill_scenario_2016}. The morphing process took into account an ensemble of 24 models for calculating projected hourly temperature, solar radiation, cloud cover, relative humidity, wind speed, and air pressure. Two climate pathways are followed, discussed in this paper as the \textit{best-case} and \textit{worst-case} scenarios. These are \textit{Shared Socioeconomic Pathway 1} (SSP126) and \textit{Shared Socioeconomic Pathway 5} (SSP585)
defined in \citet{oneill_roads_2017}. The four morphed EPWs are described in Figure \ref{fig:weatherfiles}.

@@

The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,rodriguez_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate accounts of embodied carbon. The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved. An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before seeking data from further away.

@@

\begin{figure}[hbt]
    \centering
    \includegraphics[scale=0.8]{figures/general_results_box.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

@@

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=0.8]{figures/true_maccs_waterfalls_both.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:true_macc_both}
\end{figure}

@@

\begin{figure*}[hbpt]
    \centering
    \includegraphics[scale=0.8]{figures/optimal_plots.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:pareto_plot}
\end{figure*}

@@

Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016, zeitz_comparing_2019}. This study did not consider the Mass Timber strategy to be carbon sequestering, but it is less intensive than cement-based building, leading to between 60 and 300 Tonnes of carbon abated, depending on the development scenario.

>>>>

This study will test the performance of eight strategies alongside one development pathway and two climate change pathways, simulated at two points in time (2050 and 2080), for a case study community in southwestern Canada; Wesbrook Village, Vancouver, British Columbia (BC). A baseline urban building energy model (UBEM) was created to represent the development of the community to-date.

@@

\subsection*{Wesbrook Village} 
% Simulation will be exhaustive of the different combinations in the pool of strategies and scenarios allowing each strategy to be measured independently as well as determine combinations that are more or less efficient than individual implementation under the entire range of uncertainty.
Wesbrook Village and the neighbouring Stadium Road are new communities that expected to reach 715,925 sqm. of residential floor space and 10,000 sqm. of non-residential floor space by 2040. It is the part of a larger community plan led by the development arm of The University of British Columbia (UBC) \citep{ubc_planning_ubc_2020_SR, ubc_planning_ubc_2020_wb}. The baseline for this study is taken at the end of 2020, where the development has completed its fifteenth year. The development, referred to throughout the study as \textit{Wesbrook}, is a compelling case study as it can be considered a model of medium-density new development for BC and North America at large. Building code for the community is modeled after the aspirational provincial code made more strict through a continuous review with the most recent version taking effect in January 2021 and targeting net-zero energy ready (NZER) by 2032; NZER buildings are built such that with the addition of solar panels or renewable technologies they would consume only as much energy as they produce. The energy system is a mixture of grid-connected systems, in building natural gas boilers, and a district heating system that supplies hydronic baseboard and floor heating systems as well as domestic hot water. This district heating system, described in the context of a UBEM in \citet{mccarty_accepted_2020}, is designed to switch from natural gas boilers to heat pumps amplified by waste heat from a nearby particle accelerator facility but still with peaking boilers fueled by natural gas. Cooling services have yet to considered in spec-residential development in BC as the climate has historically allowed comfort to be achieved in the peak of summer through natural ventilation; research however indicates that this may become an obsolete design standard due to climate change \citep{rysanek_forecasting_2021}. The intention with the code development for this community is that cooling will be required within a decade \citep{noauthor_residential_2021}.

@@

\subsection*{Urban Building Energy Model}
The simulation framework utilizes an extension of the City Energy Analyst (CEA) demand forecasting model \citep{fonseca_city_2016,the_cea_team_city_2020}. The CEA enables simulations of urban and neighborhood scale energy systems, as well as independently operating buildings. It is a hybrid dynamic statistical model that allows for efficient processing times, a necessity for large simulation sets such as the one in this study. These urban building energy models (UBEM) are low-level of detail geometrically described by their heights above and below ground, window to wall ratio, and composition of envelope, HVAC, and energy supply traits.

@@

The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models. The morphing process took into account an ensemble of 24 models for calculating projected hourly temperature, solar radiation, cloud cover, relative humidity, wind speed, and air pressure. Two climate pathways are followed, discussed in this paper as the \textit{best-case} and \textit{worst-case} scenarios. These are \textit{Shared Socioeconomic Pathway 1} (SSP126) and \textit{Shared Socioeconomic Pathway 5} (SSP585)
defined in \citet{oneill_roads_2017}. The four morphed EPWs are described in Figure \ref{fig:weatherfiles}.

@@

The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{jones_ice_2019, droguett_embodied_2019,c-change_labs_embodied_2020}, and are cradle-to-gate accounts of embodied carbon. The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved. An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before seeking data from further away.

@@

\begin{figure}[hbt]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.8]{figures/general_results_box.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

@@

\begin{figure}[hbpt]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.95]{figures/true_maccs_waterfalls_both.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:true_macc_both}
\end{figure}

@@

% \begin{figure*}[hbpt]
%     \centering
%     \includegraphics[scale=0.8]{figures/optimal_plots.eps}
%     \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%     \label{fig:pareto_plot}
% \end{figure*}

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=0.55]{figures/pareto_plots_585.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:pareto_plot}
\end{figure}

@@

Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016}. This study did not consider the Mass Timber strategy to be carbon sequestering, but it is less intensive than cement-based building, leading to between 60 and 300 Tonnes of carbon abated, depending on the development scenario.
